\vspace{-2.0cm}The effect of nitrogen application time on infection and development of the Wheat Streak Mosaic Virus (WSMV)

### 2015-10-22 leslieandkenny.Rnw
added a sentence about fake data in Model Refinement Section

In this section, we describe how to go through the process of model selection. As discussed in the previous sections, we recommend starting with the most complicated three-way interaction model and then assessing which terms can be removed. In general, start by considering removal of the highest order terms. \\

>>>>

In this section, we describe how to go through the process of model selection. As discussed in the previous section, we recommend starting with the most complicated  model and then assessing which terms can be removed. In general, start by considering removal of the highest order terms. \\

\noindent Warning: the results reported in this section are from simulated data. This section is meant to be used as an example that can be followed when working with the real dataset. \\
